The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-15 methods/ms.tex
Minor corrections to paper

% Figure list
% 1) fig:Coverage
% 2) fig:BGPSMontage
% 3) fig:Bandpass
% 4) fig:Array
% 5) fig:CalibrationCurves
% 6) fig:Flatfield
% 7) fig:CygnusComparison
% 8) fig:PointingCalibrators
% 9) fig:PointingModel
% 10) fig:SCUBAPointingComparison
% 11) fig:IterativeMapping
% 12) fig:Flagging
% 13) fig:GlitchDistribution
% 14) fig:PCA_Graphical
% 15) fig:Deconvolution
% 16) fig:Noise
% 17) fig:NoiseVsLongitude
% 18) fig:PCA_Filter
% 19) fig:AperturePhotometry

@@

\documentclass[12pt,preprint]{aastex}
%{emulateapj}

@@

We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm continuum survey
of \bgpsarea\ square degrees of the Galactic Plane primarily in the 1st
quadrant with some coverage in the 2nd and 3rd quadrants.  The BGPS represents
the first large area, systematic survey of the Northern Galactic Plane in the
millimeter continuum without pre-selected targets.  The survey has detected
\ncores\ clumps to a limiting depth of between \bgpsdepthlow\ and
\bgpsdepthhigh\ mJy RMS.  We include maps of 100 contiguous square degrees from
$l=-10.5$ to $l=86.5$ and $b=\pm0.5$ with a resolution of $\sim$35\arcsec, as
well as regions in IC1396, $l=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
striking feature of the maps is the filamentary structure of cold dust
throughout the Galaxy.

@@

Millimeter-wavelength continuum surveys of the Galactic plane provide
the most efficient way to find molecular clumps that are the likely sites of
formation for massive stars and star clusters. The development of
detector arrays have made blind surveys of large areas possible.
Such surveys can remove the selection effects used in previous surveyes,
such as the presence of embedded stars or star clusters, infrared sources,
masers, or radio continuum emission. In particular, they can locate
molecular clumps before stars form, providing vital information on
the initial conditions.  The surveys can also provide valuable constraints
on the physical properties of the clumps, especially masses and mean densities.

@@

Surveys of the galaxy in CO line emission \citep{dame01,FCRAO} have
identified the locations of large molecular clouds and traced
the transition from atomic to molecular gas as distance from the
center of the galaxy decreases. Together with kinematic distances
\citep[e.g.][]{RotationCurve} and, more recently, accurate distances
from VLBI (add ref to Reid et al. work), these surveys have begun to
reveal the spiral structure of the Milky Way. As this picture comes into
sharper focus, we can begin to address the old question of the relationship
between spiral density waves and star formation.

To pursue this question, we need tracers of higher density material.
Studies of nearby clouds have demonstrated that star formation is far
from uniform over molecular clouds, but is concentrated in unusually dense
regions called clumps or cores, which fill a small fraction of the area
of most clouds [refs. E. Lada et al. Evans et al., Enoch et al.]
Following \citet{williams00} and McKee-Ostriker (ARAA), we
use the term core to refer to a very dense region destined to form an
individual star or small multiple star systems and the term clump to
refer to a
region likely to form a group or cluster of stars. While clumps forming
massive clusters may be denser than cores forming low mass stars
[ref Mueller?],
in general, clumps are larger and less dense. Clumps can be traced
with line emission from molecules such as \ammonia, \form, CS, HCN, etc.
Spectral lines also provide excellent diagnostics of
line-of-sight motions, temperatures, and densities.
However, the interpretation of these gas tracers is complicated by
variations in tracer abundances caused by depletions and complex
chemical processing, uncertainties in optical depths and excitation
conditions, and the impacts of radiation fields and shocks. These
complications make the derivation of column densities, masses, and
other physical properties of star-forming clumps very difficult.
A further limitation of spectral line studies is that the tracers of
denser gas tend to be weak and multi-element receiver arrays have
only a modest number of elements, making blind surveys very time-consuming.

In contrast, focal-plane arrays containing hundreds of individual
bolometers sensitive to millimeter and sub-millimeter (sub-mm)
radiation are now available. This advance in technology enables
blind surveys of the Galactic plane, providing a uniform inventory of massive
star-forming and starless clumps.  Catalogs resulting
from such surveys will provide the data base for subsequent observations
in tracers such as hard-to-excite molecular lines and higher resolution
studies with instruments like CARMA and ALMA.
A further advantage of continuum observations of dust at long wavelengths
is the low optical depth of the dust \citep{johnstone06},
permitting a straight-forward estimate of the mass of the emitting region.

@@

Two large surveys of the Galactic plane are in progress.
The ATLASGAL survey, using the LABOCA instrument at 870 \micron\
on the APEX telescope in Chile, will cover the southern Galactic plane
and extend somewhat into the north. Initial results from this survey
have been reported by \citet{schuller09}. [say more]

This paper presents the results of the Bolocam Galactic Plane Survey
(BGPS).  (Give longitude and latitude coverage.)
It is complementary to the survey by \citet{schuller09} in that
it targets the part of the plane visible from the northern
hemisphere and uses a somewhat longer wavelength, allowing
comparison of properties in the region of overlap with the survey of
\citet{schuller09}.
At 870 \micron, $h\nu/k = 16.5$ K, compared to 13.1 K at 1.1 mm.
Because starless clumps may be quite cold ($\td \approx 10$ K),
the uncertainty in mass caused by uncertain temperature is less at 1.1 mm.
For example, the mass estimate if the actual $\td = 20$ K, rather
than 10 K, would decrease by a factor of 3.3 at 870 \micron\
versus a factor of 2.9 at 1.1 mm. In addition, the Bolocam bandpass
excludes the CO \jj{21} line, which can be a significant contaminant
on top of the dust continuum emission.

@@

% TEST
% Useful, but not here
%\begin{figure}
%  \subfigure[$l=-10.5$ to $l=19.5$ Units are Jy/Beam.  The brightest
%	sources, e.g. Sgr B2, Sgr A, and sources near $l=10$ and
%	$l=13$, appear to be saturated, but this is only a display
%	artifact.  The noise is more pronounced from $l=-7$ to $l=-2$
%	because this region was observed less.]{\label{fig:BGPSMontage-a}\includegraphics[scale=0.75]{fig1_pg1_bw_inv_bar_label}}\\
%\pagebreak
%\subfigure[$l=19.5$ to $l=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
%	51, W 43, W 49, and M 17 appear to be saturated, but this is
%	only a display artifact.]
%{\label{fig:BGPSMontage-b}\includegraphics[scale=0.75]{fig1_pg2_bw_inv_bar_label}}
%
%\end{figure}
%% --------------------------------
%

@@

%\begin{sidewaysfigure}[h]
\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
      \caption{$l=-10.5$ to $l=19.5$ Units are Jy/Beam.  The brightest
	sources, e.g. Sgr B2, Sgr A, and sources near $l=10$ and
	$l=13$, appear to be saturated, but this is only a display
	artifact.  The noise is more pronounced from $l=-7$ to $l=-2$
	because this region was observed less.}
    \end{center}
    \label{fig:BGPSMontage}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \begin{minipage}{6.5in} 
    \begin{center}
      \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
      \caption{$l=19.5$ to $l=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
	51, W 43, W 49, and M 17 appear to be saturated, but this is
	only a display artifact.  The $20 < \ell < 40$ region through the
        4-8 kpc molecular ring and approximately the termination of the galactic
        bar is particularly rich in clumps.}
    \end{center}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \begin{minipage}{6.5in} 
    \begin{center}
      \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
      \caption{$l=49.5$ to $l=74.5$.  In comparison to the inner galaxy, the $65
      < \ell < 75$ has a very sparse population of clumps}
    \end{center}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \hspace{-1in}
  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
  \caption{The Cygnus Arm. Note that coverage in \emph{b} is extended to $\pm
  1.5\deg$. The large scale 'peanut' shape including DR21 is suggestive of a
  large wind-blown bubble, although.... [someone else must have commented on
  this in the past?].  See section \ref{sec:motte} for a comparison with the
  \citet{motte07} IRAM study of this region. }
\end{figure}
%  \vspace{-4in}

@@

\begin{figure}
\hspace{-0.5in}
  \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
  \caption{Cloud complexes centered at $l=111$ in the Perseus Arm. \TBD\ Add annotations}
\end{figure}

@@

A number of different descriptions of the reduction of Bolocam data
have been published \citep{laurent05,enoch06,sayers09}.  This work
addresses the issues specific to the BGPS, significantly improving the
method of \citet{enoch06} for generating maps and characterizing their
properties.  It incorporates also some of the technical developments
of \citet{sayers09}, though the exquisite control of systematics and
noise of that analysis is neither necessary nor possible here.

@@

\Table
{llllll}
{Note:  The \citet{motte07} integration box is given in terms of pc. 
The assumed distance must be about 1.7 kpc \citep{schneider2006}  }
{
%Source  &   BGPS           &  Motte \\
%        &   peak mJy/beam  &  mJy in box (see Motte+ Table 1)
Motte Source Number &  Motte Table 1 integrated flux &  Motte scaled Jy/bm  & BGPS Jy/Bm &    Comments \\
}
{tab:CygnusComparison}
{
3  &    1.59 [0.11x0.09] & 2.61      &  2.30  &  DR 17                               \\
11 &    0.34 [0.11x0.06] & 0.48      &  0.50  &  West SW of DR21                     \\
12 &    1.63 [0.11x0.09] & 2.60      &  2.20  &    "                                 \\
16 &    0.55 [0.12x0.12] & 0.82      &  0.72  &    "                                 \\
26 &    0.34 [0.20x0.10] & 0.48      &  0.44  &    "                                 \\
29 &    0.54 [0.25x0.13] & 1.10      &  0.62  &    "                                 \\
30 &   10.54 [0.15x0.10] &13.5       &  9.80  &  W75(N)                              \\
44 &    8.43 [0.14x0.11] &14.5       & 12.7   &  DR21 (OH)                           \\
46 &   17.90 [0.08x0.03] &18.4       & 15.8   &  DR21 f-f, maser (H2O)               \\
48 &    3.72 [0.17x0.11] & 9.4       &  7.8   &  DR21 (OH)-S                         \\
51 &    2.37 [0.24x0.03] & 5.5       &  4.1   &  DR21 FIR2                           \\
53 &    1.60 [0.14x0.09] & 4.3       &  2.7   &  North of DR21  FIR3                 \\
56 &    0.60 [0.12x0.08] & 0.81      &  0.75  &  SE of DR21 47                       \\
58 &    2.73 [0.23x0.19] & 2.40      &  1.64  &  IRAS 20375+4109                     \\
59 &    0.37 [0.12x0.05] & 1.3       &  0.93  &  East of IRAS 20375+4109             \\
60 &    0.56 [0.16x0.13] & 1.00      &  0.78  &  East of IRAS 20375+4109             \\
61 &    0.23 [0.12x0.09] & 0.60      &  0.49  &  MSX 81.5168+0.01926                 \\
62 &    0.50 [0.18x0.12] & 1.23      &  0.80  &  between 63 \& IRAS 20375+4109       \\
63 &    1.09 [0.08x0.05] & 1.60      &  1.50  &  DR22                                \\
65 &    0.78 [0.16x0.12] & 1.15      &  1.10  &                                      \\
66 &    0.25 [0.15x0.06] & 0.63      &  0.76  &                                      \\
68 &    0.84 [0.10x0.10] & 1.01      &  0.94  &                                      \\
69 &    1.28 [0.47x0.18] & 1.12      &  1.20  &                                      \\
72 &    0.54 [0.28x0.13] & 0.58      &  0.47  &                                      \\
}

@@

TBD: In low s/n fields, specifically l=65 to 75, there was not enough signal to
acquire a pointing offset using cross-correlation.  In these fields the
relative pointing offset is larger and the beam is slightly larger.

@@

  \subfigure[{\it Left}: the Bolocam map in a portion of the $l=30$
  field.  {\it Right}: the SLC maps in the same region.  The green
  contours on the Bolocam map indicate the positions of the SLC
  sources.  \TBD\ {\it Do the negative bowls of either survey bunge up
  the cross-correlation?  If not, how do we deal with them?  The SCUBA
  image here has been somewhat doctored because of a large DC offset
  in the diagonal filament at center}]
  {\label{fig:SCUBAPointingComparison-a}\includegraphics[scale=0.8]
  {scuba_bolocam_l030}}

@@

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[angle=90,scale=0.6]{eachpca}
    \end{center}
  \end{minipage}
\vspace{0.25in}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[angle=90,scale=0.6]{eachpca_20iters}
    \end{center}
  \end{minipage}
  \caption{Selected images to illustrate the PCA process.  The displays are in
  Galactic coordinates with a color range from -.1 to 1.0 Jy/beam.
  {\it Top}: a grid of maps of the first 20 PCA components
displayed at the same scale.  It is clear that NCG 7538, the object
imaged, has correlated emission in each component.  There are varying
levels of correlated noise in each component, with the first through
third being the most obvious atmospheric components.  Most of the
other noise components are probably varieties of correlated
detector noise. {\it Bottom}: The same figure, but after 20
iterations.  The figure is the breakdown of the atmosphere remainder
(i.e. the raw data minus the astrophysical model) into eigenfunctions.
Very little astrophysical flux remains at any level of correlation,
though there is some at large (few arcminute) scales.}
\label{fig:PCA_Graphical}

@@

\Figure{l001_deconvolutionkernelcompare}{The effect of deconvolution
on the iterative process can be seen in its effect on the
residuals. From left to right: map, noise, smoothmap, model. Top to
bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which
has the result of leaving no flux in the residual at the location of
Sgr B2, and does not ``dig a hole'' in the residual map, as the
7.2\arcsec\ kernel does.}{fig:Deconvolution}{1.0}

@@

Figure \ref{fig:deconv_filter}b shows the fraction of flux recovered
in the maps as a function of the deconvolution kernel used to create
the astrophysical model maps.  The differences at large source sizes
are not yet well-understood (!!!!!!), but at the smallest source size,
it is evident that a deconvolution kernel smaller than the source size
does not reliably recover the source flux.  Therefore we chose a
deconvolution kernel smaller than the beam but larger than the pixel
size used.  Figure \ref{fig:Deconvolution} demonstrates the effects of
using both too large and too small a kernel.

@@

\FigureTwo{pca_comparison_l111}{deconvolution_comparison_l111}{The
fractional flux recovered as a function of source size for
well-separated Gaussian sources with the FWHM as indicated.
\emph{Left}: 3 (blue),7 (green),10 (yellow) ,13 (orange),16 (red),21
(teal),26 (lime),31 (black) PCA components subtracted.  \emph{Right}:
7.2" (cyan), 14.4" (black), 21.6" (red), 31.2" (green) deconvolution
kernel for 13 PCA components subtracted. \TBD\ {\it Remove sources
with sizes smaller than the beam.  Are the sizes FWHM or something
else?} }{fig:PCA_Filter}{1.0}

@@

There are clear maxima in the emission filling factor in the Galactic
Center and in the region from $l=23$ to $l=31$, the line of sight
through the densest part of the molecular ring.  Additional areas of
high source density are seen at $l=10$ and $l=13$.  The filling factor
of 1.1 mm continuum emission at the 100 mJy level is $\sim 20$\% per
square degree from $l=-10$ to $l=20$ and $\sim 10$\% from $l=20$ to
$l=50$.
%In the range
%$l=50$ to $l=75$, the filling factor is below 1\% and very few sources have
%been detected.  
This result is in contrast to CO filling factors $\sim1$ in the inner galactic
plane \citep{dame01,FCRAO}, confirming that 1.1 mm continuum emission traces
denser material than CO.  
%The small filling factor of the 1.1 mm emission
%compared to CO emission  shows that the continuum is directly associated with
%star forming material, whereas the CO also traces less dense material not
%directly associated with star formation.

>>>>

% Figure list
% 1) fig:Coverage
% 2) fig:BGPSMontage
% 3) fig:Bandpass
% 4) fig:Array
% 5) fig:CalibrationCurves
% 6) fig:Flatfield
% 7) fig:CygnusComparison
% 8) fig:PointingCalibrators
% 9) fig:PointingModel
% 10) fig:SCUBAPointingComparison
% 11) fig:IterativeMapping
% 12) fig:Flagging
% 13) fig:GlitchDistribution
% 14) fig:PCA_Graphical
% 15) fig:Deconvolution
% 16) fig:Noise
% 17) fig:NoiseVsLongitude
% 18) fig:PCA_Filter
% 19) fig:AperturePhotometry
% 19) fig:sampleimages

@@

\documentclass[12pt,preprint]{aastex}
%\documentclass{emulateapj}

@@

We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm continuum survey
of \bgpsarea\ square degrees of the Galactic Plane primarily in the 1st
quadrant with some coverage in the 2nd and 3rd quadrants.  The BGPS represents
the first large area, systematic survey of the Northern Galactic Plane in the
millimeter continuum without pre-selected targets.  The survey has detected
\ncores\ clumps to a limiting depth of between \bgpsdepthlow\ and
\bgpsdepthhigh\ mJy RMS.  We include maps of 100 contiguous square degrees from
$\lon=-10.5$ to $\lon=86.5$ and $b=\pm0.5$ with a resolution of $\sim$35\arcsec, as
well as regions in IC1396, $\lon=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
striking feature of the maps is the filamentary structure of cold dust
throughout the Galaxy.

@@

Millimeter-wavelength continuum surveys of the Galactic plane provide the most
efficient way to find molecular clumps that are the likely sites of formation
for massive stars and star clusters. The development of detector arrays have
made blind surveys of large areas possible.  Such surveys bypass the need for
selection based on the presence of embedded stars or star clusters, infrared
sources, masers, or radio continuum emission. In particular, they can locate
molecular clumps before stars form, providing vital information on the initial
conditions of star formation.  These surveys can also provide valuable
constraints on the physical properties of the clumps, especially masses and
mean densities.

@@

Surveys of the galaxy in CO line emission \citep{dame01,FCRAO} have
identified the locations of large molecular clouds and traced
the transition from atomic to molecular gas as distance from the
center of the galaxy decreases. Together with kinematic distances
\citep[e.g.][]{RotationCurve} and, more recently, accurate distances
from VLBI \citep{reid09}, these surveys have begun to
reveal the spiral structure of the Milky Way. As this picture comes into
sharper focus, we can begin to address the old question of the relationship
between spiral density waves and star formation.

To pursue this question, we need tracers of higher density material.
Studies of nearby clouds have demonstrated that star formation is far
from uniform over molecular clouds, but is concentrated in unusually dense
regions called clumps or cores, which fill a small fraction of the area
of most clouds [refs. E. Lada et al. Evans et al., Enoch et al.]
Following \citet{williams00} and McKee-Ostriker (ARAA), we
use the term `core' to refer to a very dense region destined to form an
individual star or small multiple star systems and the term `clump' to
refer to a
region likely to form a group or cluster of stars. While clumps forming
massive clusters may be denser than cores forming low mass stars
[ref Mueller?],
in general, clumps are larger and less dense. Clumps can be traced
with line emission from molecules such as \ammonia, \form, CS, HCN, etc.
Spectral lines also provide excellent diagnostics of
line-of-sight motions, temperatures, and densities.
However, the interpretation of these gas tracers is complicated by
variations in tracer abundances caused by depletions and complex
chemical processing, uncertainties in optical depths and excitation
conditions, and the impacts of radiation fields and shocks. These
complications make the derivation of column densities, masses, and
other physical properties of star-forming clumps very difficult.
A further limitation of spectral line studies is that the tracers of
denser gas tend to be weak and multi-element receiver arrays have
only a modest number of elements, making blind surveys very time-consuming.

% redundant:
% In contrast, focal-plane arrays containing hundreds of individual
% bolometers sensitive to millimeter and sub-millimeter (sub-mm)
% radiation are now available. This advance in technology enables
% blind surveys of the Galactic plane, providing a uniform inventory of massive
% star-forming and starless clumps.  Catalogs resulting
% from such surveys will provide the data base for subsequent observations
% in tracers such as hard-to-excite molecular lines and higher resolution
% studies with instruments like CARMA and ALMA.
(this line belongs somewhere)
A further advantage of continuum observations of dust at long wavelengths
is the low optical depth of the dust \citep{johnstone06},
permitting a straight-forward estimate of the mass of the emitting region.

@@

Two large surveys of the Galactic plane are in progress.
The ATLASGAL survey, using the LABOCA instrument at 870 \micron\
on the APEX telescope in Chile, will cover the southern Galactic plane
and extend somewhat into the north. Initial results from this survey
have been reported by \citet{schuller09}. [say more - overlap region?
]

This paper presents the results of the Bolocam Galactic Plane Survey (BGPS).
The survey covers the contiguous range $-10.5 < \lon < 86.5, -.5 < b < .5$ with
additional coverage to higher $|b|$ in the range $77 < \lon < 86.5$ and in the
$\lon=111$, W3/4/5, Gem OB1, and IC 1396 regions.  It is complementary to the
survey by \citet{schuller09} in that it targets the part of the plane visible
from the northern hemisphere and uses a somewhat longer wavelength, allowing
comparison of properties in the region of overlap with the ATLASGAL survey.
At 870 \micron, $h\nu/k = 16.5$ K, compared to 13.1 K at 1.1 mm.  Because
starless clumps may be quite cold ($\td \approx 10$ K), the uncertainty in mass
caused by uncertain temperature is slightly less at 1.1 mm.  For example, the
mass estimate if the actual $\td = 20$ K, rather than 10 K, would decrease by a
factor of 3.3 at 870 \micron\ versus a factor of 2.9 at 1.1 mm. In addition,
the Bolocam bandpass excludes the CO \jj{2}{1} line, which can be a significant
contaminant on top of the dust continuum emission.

@@

% TEST
% Useful, but not here
%\begin{figure}
%  \subfigure[$\lon=-10.5$ to $\lon=19.5$ Units are Jy/Beam.  The brightest
%	sources, e.g. Sgr B2, Sgr A, and sources near $\lon=10$ and
%	$\lon=13$, appear to be saturated, but this is only a display
%	artifact.  The noise is more pronounced from $\lon=-7$ to $\lon=-2$
%	because this region was observed less.]{\label{fig:BGPSMontage-a}\includegraphics[scale=0.75]{fig1_pg1_bw_inv_bar_label}}\\
%\pagebreak
%\subfigure[$\lon=19.5$ to $\lon=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
%	51, W 43, W 49, and M 17 appear to be saturated, but this is
%	only a display artifact.]
%{\label{fig:BGPSMontage-b}\includegraphics[scale=0.75]{fig1_pg2_bw_inv_bar_label}}
%
%\end{figure}
%% --------------------------------
%

@@

%\begin{sidewaysfigure}[h]
\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
      \caption{$\lon=-10.5$ to $\lon=19.5$ Units are Jy/Beam.  The brightest
	sources, e.g. Sgr B2, Sgr A, and sources near $\lon=10$ and
	$\lon=13$, appear to be saturated, but this is only a display
	artifact.  The noise is more pronounced from $\lon=-7$ to $\lon=-2$
	because this region was observed less.}
    \end{center}
    \label{fig:BGPSMontage}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \begin{minipage}{6.5in} 
    \begin{center}
      \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
      \caption{$\lon=19.5$ to $\lon=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
	51, W 43, W 49, and M 17 appear to be saturated, but this is
	only a display artifact.  The $20 < \ell < 40$ region through the
        4-8 kpc molecular ring and approximately the termination of the galactic
        bar is particularly rich in clumps.}
    \end{center}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \begin{minipage}{6.5in} 
    \begin{center}
      \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
      \caption{$\lon=49.5$ to $\lon=74.5$.  In comparison to the inner galaxy, the $65
      < \ell < 75$ has a very sparse population of clumps}
    \end{center}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \hspace{-1in}
  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
  \caption{The Cygnus Arm. Note that coverage in \emph{b} is extended to $\pm
  1.5\deg$. The large scale `peanut' shape including DR21 is suggestive of a
  large wind-blown bubble, although.... [someone else must have commented on
  this in the past?].  See section \ref{sec:motte} for a comparison with the
  \citet{motte07} IRAM study of this region. }
\end{figure}
%  \vspace{-4in}

@@

\begin{figure}
\hspace{-0.5in}
  \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
  \caption{Cloud complexes centered at $\lon=111$ in the Perseus Arm. \TBD\ Add annotations}
\end{figure}

@@

A number of different descriptions of the reduction of Bolocam data
have been published \citep{laurent05,enoch06,sayers09}.  This work
addresses the issues specific to the BGPS, significantly improving the
method of \citet{enoch06} for generating maps and characterizing their
properties.  It incorporates some of the technical developments
of \citet{sayers09}, though the exquisite control of systematics and
noise of that analysis is neither necessary nor possible here.

@@

\Table
{llllll}
{Comparison of \citet{motte07} IRAM measurements to BGPS measurements
in the Cygnus X region
%Note:  The \citet{motte07} integration box is given in terms of pc. 
%The assumed distance must be about 1.7 kpc \citep{schneider2006}    % no, it's 1.7kpc stated explicitly
}
{
%Source  &   BGPS           &  Motte \\
%        &   peak mJy/beam  &  mJy in box (see Motte+ Table 1)
Motte Source Number &  Motte Table 1 integrated flux &  Motte scaled Jy/bm  & BGPS Jy/Bm &    Comments \\
}
{tab:CygnusComparison}
{
3  &    1.59 [0.11x0.09] & 2.61      &  2.30  &  DR 17                               \\
11 &    0.34 [0.11x0.06] & 0.48      &  0.50  &  West SW of DR21                     \\
12 &    1.63 [0.11x0.09] & 2.60      &  2.20  &    "                                 \\
16 &    0.55 [0.12x0.12] & 0.82      &  0.72  &    "                                 \\
26 &    0.34 [0.20x0.10] & 0.48      &  0.44  &    "                                 \\
29 &    0.54 [0.25x0.13] & 1.10      &  0.62  &    "                                 \\
30 &   10.54 [0.15x0.10] &13.5       &  9.80  &  W75(N)                              \\
44 &    8.43 [0.14x0.11] &14.5       & 12.7   &  DR21 (OH)                           \\
46 &   17.90 [0.08x0.03] &18.4       & 15.8   &  DR21 f-f, maser (H2O)               \\
48 &    3.72 [0.17x0.11] & 9.4       &  7.8   &  DR21 (OH)-S                         \\
51 &    2.37 [0.24x0.03] & 5.5       &  4.1   &  DR21 FIR2                           \\
53 &    1.60 [0.14x0.09] & 4.3       &  2.7   &  North of DR21  FIR3                 \\
56 &    0.60 [0.12x0.08] & 0.81      &  0.75  &  SE of DR21 47                       \\
58 &    2.73 [0.23x0.19] & 2.40      &  1.64  &  IRAS 20375+4109                     \\
59 &    0.37 [0.12x0.05] & 1.3       &  0.93  &  East of IRAS 20375+4109             \\
60 &    0.56 [0.16x0.13] & 1.00      &  0.78  &  East of IRAS 20375+4109             \\
61 &    0.23 [0.12x0.09] & 0.60      &  0.49  &  MSX 81.5168+0.01926                 \\
62 &    0.50 [0.18x0.12] & 1.23      &  0.80  &  between 63 \& IRAS 20375+4109       \\
63 &    1.09 [0.08x0.05] & 1.60      &  1.50  &  DR22                                \\
65 &    0.78 [0.16x0.12] & 1.15      &  1.10  &                                      \\
66 &    0.25 [0.15x0.06] & 0.63      &  0.76  &                                      \\
68 &    0.84 [0.10x0.10] & 1.01      &  0.94  &                                      \\
69 &    1.28 [0.47x0.18] & 1.12      &  1.20  &                                      \\
72 &    0.54 [0.28x0.13] & 0.58      &  0.47  &                                      \\
}

@@

TBD: In low s/n fields, specifically \lon=65 to 75, there was not enough signal to
acquire a pointing offset using cross-correlation.  In these fields the
relative pointing offset is larger and the beam is slightly larger.

@@

  \subfigure[{\it Left}: the Bolocam map in a portion of the $\lon=30$
  field.  {\it Right}: the SLC maps in the same region.  The green
  contours on the Bolocam map indicate the positions of the SLC
  sources.  \TBD\ {\it Do the negative bowls of either survey bunge up
  the cross-correlation?  If not, how do we deal with them?  The SCUBA
  image here has been somewhat doctored because of a large DC offset
  in the diagonal filament at center}]
  {\label{fig:SCUBAPointingComparison-a}\includegraphics[scale=0.8]
  {scuba_bolocam_l030}}

@@

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[angle=270,scale=0.6]{eachpca}
    \end{center}
  \end{minipage}
\vspace{0.25in}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[angle=270,scale=0.6]{eachpca_20iters}
    \end{center}
  \end{minipage}
  \caption{Selected images to illustrate the PCA process.  The displays are in
  Galactic coordinates with a color range from -.1 to 1.0 Jy/beam.
  {\it Top 4 rows}: a grid of maps of each of the first 20 PCA components displayed at
  the same scale.  It is clear that NCG 7538, the object imaged, has emission
  in each component.  There are varying levels of noise in each component, with
  the first and second being the most obvious atmospheric components.  Most of
  the other noise components are probably detector noise correlated among a
  subset of the bolometers.  The streaks are residuals of the scan-turnaround
  noise that was not removed by the exponential model fit.  {\it Bottom 4
  rows}: The same figure, but after 20 iterations.  The figure is the breakdown
  of the atmosphere remainder (i.e.  the raw data minus the astrophysical
  model) into eigenfunctions.  Very little astrophysical flux remains at any
  level of correlation, though there is some at large (few arcminute) scales.}
\label{fig:PCA_Graphical}

@@

\Figure{l001_deconvolutionkernelcompare}{The effect of deconvolution
on the iterative process can be seen in its effect on the
residuals. From left to right: map, noise, model. Top to
bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which
has the result of leaving no flux in the residual at the location of
Sgr B2, and does not ``dig a hole'' in the residual map, as the
7.2\arcsec\ kernel does.  The 7.2\arcsec\ kernel also lacks the
noise-rejection features of the larger kernels, as can be seen in the
last panel.}{fig:Deconvolution}{1.0}

@@

Figure \ref{fig:deconv_filter}b shows the fraction of flux recovered in the
maps as a function of the deconvolution kernel used to create the astrophysical
model maps.  The differences at large source sizes are not well-understood
(these size scales may be dominated by atmosphere), but at the smallest source
size, it is evident that a deconvolution kernel smaller than the source size
does not reliably recover the source flux.  Therefore we chose a deconvolution
kernel smaller than the beam but larger than the pixel size used.  Figure
\ref{fig:Deconvolution} demonstrates the effects of using both too large and
too small a kernel.

@@

\FigureTwo{pca_comparison_nolegend_l111}{deconvolution_comparison_nolegend_l111}{The
fractional flux recovered as a function of source size for
well-separated Gaussian sources with the FWHM as indicated.
\emph{Left}: 3 (blue), 7 (green), 10 (yellow), 13 (orange), 16 (red), 21
(teal), 26 (lime), 31 (black) PCA components subtracted.  
Note that flux recovery drops to 50\% at 120\arcsec for the 13 PCA
component cleaning used in the released data.  The 3 and 7 PCA cases
show bumps because atmospheric noise is still present at large scales.
The $>$100\% recovery for sources smaller than the deconvolution kernel is a
side-effect; since the deconvolution kernel is smaller than the beam, no real
source should ever be smaller than the kernel.
\emph{Right}:
7.2\arcsec (cyan), 14.4\arcsec (black), 21.6\arcsec (red), 31.2\arcsec (green)
deconvolution kernel for 13 PCA components subtracted.  It is clear that the
larger deconvolution kernels generate spurious signal at smaller scales, but
the flux recovery is very close to 1 at the beam size
(35\arcsec)}{fig:PCA_Filter}{1.0}

@@

There are clear maxima in the emission filling factor in the Galactic
Center and in the region from $\lon=23$ to $\lon=31$, the line of sight
through the densest part of the molecular ring.  Additional areas of
high source density are seen at $\lon=10$ and $\lon=13$.  The filling factor
of 1.1 mm continuum emission at the 100 mJy level is $\sim 20$\% per
square degree from $\lon=-10$ to $\lon=20$ and $\sim 10$\% from $\lon=20$ to
$\lon=50$.
%In the range
%$\lon=50$ to $\lon=75$, the filling factor is below 1\% and very few sources have
%been detected.  
This result is in contrast to CO filling factors $\sim1$ in the inner galactic
plane \citep{dame01,FCRAO}, confirming that 1.1 mm continuum emission traces
denser material than CO.  
%The small filling factor of the 1.1 mm emission
%compared to CO emission  shows that the continuum is directly associated with
%star forming material, whereas the CO also traces less dense material not
%directly associated with star formation.
